---
title: "sentiment_analysis"
author: "Andrew Altuna & Bernard Diamante"
date: "12/31/2020"
output: html_document
---

## Load libraries
```{r}
library(tidytext)
library(tidyverse)
library(dplyr)
library(wordcloud2)
```

## Load in master_dataset and filter dates
```{r}
md <- cleaned_master_dataset
md$created_at <- as.Date(md$created_at)

md <- md %>%
  filter(!(created_at <= "2020-11-28")) %>%
  filter(!(created_at == "2020-12-05"))
```

## Tokenize words and extract word and date columns
```{r}
word_date <- md %>%
   unnest_tokens(input = stripped_punctuations, output = word) %>%
   select(created_at,word)
```

## Filtering out custom stop words
```{r}
custom_stop_words <- tibble(word = c("trump", "poverty", "hedge", "conservative", "inequality", "rhetoric", "nominate", "management", "cabinet", "government", "pick", "director", "council", "president", "elect", "budget", "confirmed", "center", "team", "pay", "labor", "senate", "trade", "white", "deputy", "horse", "committee", "cap", "policy", "rod", "spokesman", "extra", "john", "nomination" ), lexicon = c("custom"))

word_date <- word_date %>%
   anti_join(custom_stop_words, by="word")
```

## Sentiment scores per word per day

### Bing Lexicon
```{r}
bing_worddate <- word_date %>%
   inner_join(get_sentiments("bing"), by = "word") %>%
   count(word, date = created_at, sentiment) %>%
   spread(sentiment, n,  fill = 0) %>%
   mutate(sentiment = positive - negative, n = positive + negative)
  
bing_totalsenti <- aggregate(bing_worddate[ , 3:5], FUN="sum", list(date = bing_worddate$date))
```

### AFINN Lexicon
```{r}
afinn_worddate <- word_date %>%
   inner_join(get_sentiments("afinn"), by = "word") %>%
   count(word, date = created_at, value) %>%
   mutate(sentiment = value * n)
   
afinn_totalsenti <- aggregate(afinn_worddate[ , 5], FUN="sum", list(date = afinn_worddate$date))%>%
   rename(sentiment = x)
```

## Visualizations

### Bing
### This code generates the figure for "Sentiment of Twitter Users Towards Tanden Over Time (Bing)"
```{r}
ggplot(bing_totalsenti, aes(x = date, y = sentiment, fill = "Sentiment")) +
  geom_col(show.legend = FALSE) +
  #labs(caption="Figure x.x: Sentiment of Twitter Users Towards Tanden Over Time (Bing)") + 
  theme(plot.caption = element_text(hjust=0.5, size=rel(0.9)))
ggsave("over_time_bing.png")
```
### AFINN
### This code generates the figure for "Sentiment of Twitter Users Towards Tanden Over Time (AFINN)"
```{r}
ggplot(afinn_totalsenti, aes(x = date, y = sentiment, fill = "Sentiment")) +
  geom_col(show.legend = FALSE) +
  #labs(caption="Figure x.x: Sentiment of Twitter Users Towards Tanden Over Time (AFINN)") +
  theme(plot.caption = element_text(hjust=0.5, size=rel(0.9)))
ggsave("over_time_afinn.png")
```
## Contribution to sentiment

### Bing
### This code generates the figure for Top 10 Words with Largest Contribution per Sentiment (Bing)
```{r}
bing_word_counts <- word_date %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_word_counts %>%
   group_by(sentiment) %>%
   slice_max(order_by = n, n = 10) %>%
   ungroup() %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(x = "contribution to sentiment",
       y = NULL) +
  #labs(caption="Figure x.x: Top 10 Words with Largest Contribution per Sentiment (Bing)") +
  theme(plot.caption = element_text(hjust=0.5, size=rel(0.9)))
ggsave("top10_bing.png")
```
### AFINN
### This code generates the figure for Top 10 Words with Largest Contribution per Sentiment (AFINN)
```{r}
afinn_wordtotals <- aggregate(afinn_worddate[ , 5], FUN="sum", list(word = afinn_worddate$word)) %>%
   rename(sentiment = x)

sent <- ifelse(afinn_wordtotals$sentiment > 0, "positive", "negative")

afinn_wordtotals <- cbind(sent,afinn_wordtotals)
afinn_wordtotals$sentiment <- abs(afinn_wordtotals$sentiment)

afinn_wordtotals %>%
   group_by(sent) %>%
   slice_max(order_by = sentiment, n = 10) %>%
   ungroup() %>%
  mutate(word = reorder(word, sentiment)) %>%
   
  ggplot(aes(sentiment, word, fill = sent)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sent, scales = "free_y") +
  labs(x = "contribution to sentiment",
       y = NULL) +
  #labs(caption="Figure x.x: Top 10 Words with Largest Contribution per Sentiment (AFINN)") + 
  theme(plot.caption = element_text(hjust=0.5, size=rel(0.9)))
ggsave("top10_afinn.png")
```
### NRC (Moods)
### This code generates the figure for Cumulative Mood Counts (NRC)
```{r}
nrc_worddate <- word_date %>%
   inner_join(get_sentiments("nrc"), by = "word") %>%
   count(word, date = created_at, sentiment) %>%
   spread(sentiment, n,  fill = 0) %>%
   mutate(sentiment = positive - negative, n = positive + negative)

nrc_wordtotals <- aggregate(nrc_worddate[ , 3:12], FUN="sum", list(word = nrc_worddate$word)) %>%
   select(c(2:11)) %>%
   colSums() %>%
   data.frame()
   
rnames <- rownames(nrc_wordtotals)

nrc_wordtotals <- mutate(nrc_wordtotals, Mood = rnames)
colnames(nrc_wordtotals) <- c("count","mood")
nrc_wordtotals <- nrc_wordtotals[order(nrc_wordtotals$count),]

ggplot(nrc_wordtotals, aes(x = mood, y = count, fill = mood)) +
  geom_col(show.legend = FALSE) +
  #labs(caption="Figure x.x: Mood of Twitter Users Towards Tanden") + 
  theme(plot.caption = element_text(hjust=0.5, size=rel(0.9)))
ggsave("mood_count.png")
```